Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-04-29 article-00-headers.tex
Updates from ShareLaTeX
Reduced number of headings

% TODO text
\newcommand{\TODO}[1]{\highlight{\textbf{TODO: }{#1}}}

@@

\newcommand{\ifcowl}{\textbf{ifcOWL}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}

@@

The volume of data produced in the construction industry is rapidly growing but, as of now, it is not available for open and flexible access and utilization. We present an ontology derived from the conceptualization of IFC, the existing standard for representing building designs, and a tool to convert building designs from IFC files to RDF datasets that conform to the ontology. Replacing the traditional point-to-point exchange of IFC files with publication of RDF datasets  by using Linked Data principles and tools enables information integration across different IFC-based and other smart city datasets, and the granular access to individual components. It paves the way to a distributed and loosely coupled architecture for building information management. Opening selected parts of construction data to a wider set of stakeholders creates opportunities for innovative applications in the smart cities of the future.

>>>>

% TODO text
% \newcommand{\TODO}[1]{\highlight{\textbf{TODO: }{#1}}}
\newcommand{\TODO}[1]{{}}

@@

\newcommand{\ifcowl}{\textbf{ifcOWL}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}
\newcommand{\ifcrdf}{\textbf{ifcRDF}}

@@

The volume of data produced in the construction industry is rapidly growing but, as of now, it is not available for open and flexible access and utilization. We present an ontology derived from the conceptualization of IFC, the existing standard for representing building designs, and a tool to convert building designs from IFC files to RDF datasets that conform to the ontology. Replacing the traditional point-to-point exchange of IFC files with publication of RDF datasets using Linked Data principles and tools enables information integration across different IFC-based and other smart city datasets, and the granular access to individual components. It paves the way to a distributed and loosely coupled architecture for building information management, and provides opportunities for innovative applications.

### 2015-04-29 article-01-introduction.tex
Updates from ShareLaTeX
Reduced number of headings

Currently, huge amounts of information about building designs is produced  
using Building Information Modeling (BIM) tools. A widely adopted standard, 
IFC (Industry Foundation Classes) provides a common representation for BIM models developed in 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

BIM models could provide a natural framework to organize and manage information gathered from other 
sources. However, a big obstacle is the difficulty to access and utilize BIM models. 
In the realm of IFC the sharing of building models is based on point-to-point file exchange which 
requires repeated manual work from designers. Information cannot be used in an online, granular, and 
interlinked manner which provides a poor basis for open utilization of building information and the 
emergence of new, innovative applications.

To make building designs more openly accessible over the Web, we have developed the 
\emph{WebIFC converter} to 
derive OWL ontologies from the IFC schema (\ifcowl{}), and RDF datasets from IFC files 
(\ifcrdf{}). The ifcOWL ontology is used to classify concepts, characterize possible relationships, 
and define constraints in \ifcrdf{} datasets which replicate the content of original IFC data files. 
All terms defined in the \ifcowl{} ontology must therefore be based on the corresponding constructs in 
the original IFC schema. The conversion from IFC data files to RDF is straightforward and can be done 
without information loss.

Ideally, there should also be just one \ifcowl{} ontology for each version of the IFC schema. However,
there are possibilities and reasons to convert the IFC schema to OWL in several different ways for
the following reasons. Firstly, there is a \emph{mismatch} between the modeling constructs of OWL and 
EXPRESS data definition language used to specify the IFC schema, which creates
different conversion options. Secondly, a simple version of \ifcowl{} \emph{compatible with
restricted OWL profiles} (OWL 2 EL or QL) is useful to support ontology
reasoning or inexact reasoning. Thirdly, for most practical purposes only a subset of ontology
information is ever required, since no validation or checking of \ifcrdf{} data is needed; it can
be considered \emph{practically valid} with respect to the schema, since IFC files are exported
from BIM tools with certified converters, and icfRDF can sensibly only be used in a
\emph{read-only} fashion, since BIM models will be maintained in the native formats of BIM
tools. Fourthly, a full conversion of the IFC schema will make \ifcowl{}
\emph{unnecessarily large}, and difficult to understand or manipulate.

\begin{figure}[h]
\centering
\includegraphics[angle=0,width=1.0\textwidth]{images/ifcOWL-multilayers.png}
%\includegraphics{images/ifcOWL-multilayers.jpg}
\caption{Multiple layers of \ifcowl{} ontology}
\label{fig:ifcOWL-layers}
\end{figure}

Consequently, we have converted the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}). 
New representational constructs are introduced at more comprehensive levels which therefore 
provide increasing detailed type information about \ifcrdf{} data. Different levels of details of the \ifcowl{} ontology are the following:

\noindent
\begin{tabular}{|l|l|l|}
\hline
\textbf{Layer} & Profiles & Included schema information \\
\hline
\hline
\name{ifcOWL-Simple} & OWL 2 EL & Schema meta data \\
& OWL 2 QL &  All type definitions and hierarchies \\
& OWL 2 RL & All entity type properties (names, range types) \\
\hline 
\name{ifcOWL-Standard} & OWL 2 RL & Schema meta data \\
& & All entity type keys \\
& & All entity type inverse properties \\
\hline
\name{ifcOWL-Extended} & OWL 2 RL & All cardinality constraints of properties \\
& & All cardinality constraints of list types \\
\hline
\end{tabular}

Since all \ifcrdf{} datasets are compatible with all layers of the \ifcowl{} ontology 
(Fig. \ref{fig:ifcOWL-layers}), a user can choose the best one based on the requirements of 
the concrete use case and tools. For instance, many Linked Data applications that need to 
query entity properties, extract the type hierarchy, or convert \ifcrdf{} datasets back to 
object-oriented data models it is sufficient to use the \name{ifcOWL-Simple} ontology. 
In case of reasoning about data that includes inverse properties, it is recommended to use 
\name{ifcOWL-Standard} ontology. If an RDF dataset needs to be modified and data validated 
using type and cardinality constraints, \name{ifcOWL-Extended} ontology is the correct choice.

>>>>

Currently, huge amounts of information about building designs is produced  
using Building Information Modeling (BIM) tools \cite{eastman2011bim}. A widely adopted standard, 
IFC (Industry Foundation Classes) \cite{ISO16739,liebich2010unveiling} provides a common representation for BIM models of 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

BIM models could provide a natural framework to organize and manage information about buildings. However, a big obstacle is the difficulty to access and utilize BIM models which have traditionally been shared shared through point-to-point file exchange. They cannot be used in an online, granular, and 
interlinked manner and provides a poor basis for open utilization of building information and the 
emergence of new, innovative applications.
To make BIM models accessible on the Web \cite{torma2014wobd}, we have developed the 
\name{WebIFC converter} to 
derive OWL ontologies from the IFC schema (\ifcowl{}), and RDF datasets from IFC files 
(\ifcrdf{}). The \ifcowl{} specifies concepts, relations, and constraints for \ifcrdf{} datasets that replicate the content of IFC files. 
All terms defined in \ifcowl{}  must thus be based on the corresponding constructs in 
the IFC schema.

\begin{figure}[h]
\centering
\includegraphics[angle=0,width=0.9\textwidth]{images/ifcOWL-multilayers.png}
%\includegraphics{images/ifcOWL-multilayers.jpg}
\caption{Multiple layers of \ifcowl{} ontology}
\label{fig:ifcOWL-layers}
\end{figure}

The conversion of IFC files to \ifcrdf{} is straightforward and can be done 
without information loss.
Ideally, there would also be just one \ifcowl{} ontology for each version of the IFC schema. However,
there are possibilities and reasons to convert the IFC schema to OWL in several different ways. Firstly, there is a \emph{mismatch} between the modeling constructs of OWL and 
EXPRESS data definition language used to specify the IFC schema. Secondly, a simple version of \ifcowl{} \emph{compatible with
restricted OWL profiles} (OWL 2 EL or QL) \cite{motik2009owl} is useful to support ontology
reasoning or inexact reasoning. Thirdly, for most practical purposes only a subset of ontology
information is required, as no validation or checking of \ifcrdf{} data is needed; it can
be considered \emph{practically valid} w.r.t. the schema, since BIM tools use certified converters, and icfRDF can sensibly only be used in a
\emph{read-only} fashion, since BIM models will be maintained in the native formats of BIM
tools. Fourthly, a full conversion of the IFC schema will make \ifcowl{}
\emph{unnecessarily large}, and difficult to understand or manipulate.

Consequently, we convert the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}). 
New representational constructs are introduced at more comprehensive levels which therefore 
provide increasing detailed type information about \ifcrdf{} data:

\vspace{2mm}
% \noindent
\begin{small}
\begin{tabular}{|l|l|l|}
 \hline
\textbf{Layer} & \textbf{Profiles} & \textbf{Included schema information} \\
\hline
 \hline
\name{ifcOWL-Simple} & OWL 2 EL & Schema meta data \\
& OWL 2 QL &  All type definitions and hierarchies \\
& OWL 2 RL & All entity type properties (names, range types) \\
\hline 
\name{ifcOWL-Standard} & OWL 2 RL & Schema meta data \\
& & All entity type keys \\
& & All entity type inverse properties \\
\hline
\name{ifcOWL-Extended} & OWL 2 RL & All cardinality constraints of properties \\
& & All cardinality constraints of list types \\
 \hline
\end{tabular}
\end{small}

%Since all \ifcrdf{} datasets are compatible with all layers of the \ifcowl{} ontology 
%(Fig. \ref{fig:ifcOWL-layers}), the most appropriate one can be selected based on the requirements of 
%a use case and tools. For instance, many Linked Data applications that need to 
%query entity properties, use the type hierarchy, or convert \ifcrdf{} datasets back to 
%object-oriented data models it is sufficient to use the \name{ifcOWL-Simple} ontology. 
%In case of reasoning about data that includes inverse properties, it is recommended to use 
%\name{ifcOWL-Standard} ontology. If an RDF dataset needs to be modified and data validated 
%using type and cardinality constraints, \name{ifcOWL-Extended} is the correct choice.

From the previous IFC-to-OWL/RDF conversions
\cite{beetz2005ontology,beetz2009ifcowl,pauwels2011interoperability} our approach differs since it
is based on OWL 2 profiles, produces a flexible multilayer ontology, and is specifically targeted to
real-life Linked Data applications. It uses stable URIs for entities, in contrast to the previous approaches
where the URIs were instable across models versions.
